Active deformation of the Shargyn Basin, a transpressional strike-slip intersection in western Mongolia.

### 2013-10-07 writing/jaes_article/abstract.tex
starting jaes article

\begin{abstractpage}
Intraplate faulting in central Asia is a major component of the Indo-Eurasian collision. The kinematics and mechanisms of intraplate deformation are important in understanding broad active tectonic patterns, reconstructing past tectonics, analyzing seismic hazard and identifying potential resources. We examine the fault kinematics surrounding the 150 km wide Shargyn Basin at the intersection of the left-lateral transpressional Gobi-Altai fault system and the right-lateral transpressional Altai fault system. The studies were performed using satellite data and targeted field transects. The results suggest the Shargyn basin is formed by a compressional stepover, an uplifted wedge from the intersecting strike-slip systems and many strike-slip terminating thrust splays. Furthermore, local foliation is almost always fault parallel, pointing to the importance of pre-existing structural weaknesses in the development of active faults. This research demonstrates some of the potential kinematics for intraplate transpressional orogenies and emphasizes the importance of pre-existing crustal structure in the development of active faults.
\end{abstractpage}

>>>>

\begin{abstract}
Intraplate faulting in central Asia is a major component of the Indo-Eurasian collision. The kinematics and mechanisms of intraplate deformation are important in understanding broad active tectonic patterns, reconstructing past tectonics, analyzing seismic hazard and identifying potential resources. We examine the fault kinematics surrounding the 150 km wide Shargyn Basin at the intersection of the left-lateral transpressional Gobi-Altai fault system and the right-lateral transpressional Altai fault system. The studies were performed using satellite data and targeted field transects. The results suggest the Shargyn basin is formed by a compressional stepover, an uplifted wedge from the intersecting strike-slip systems and many strike-slip terminating thrust splays. Furthermore, local foliation is almost always fault parallel, pointing to the importance of pre-existing structural weaknesses in the development of active faults. This research demonstrates some of the potential kinematics for intraplate transpressional orogenies and emphasizes the importance of pre-existing crustal structure in the development of active faults.

Keywords: Intraplate Faulting, Basin Kinematics, Transpressional Strike-slip, Altai Fault System, Gobi-Altai Fault System
\end{abstract}

### 2013-10-07 writing/jaes_article/background.tex
starting jaes article

\begin{figure}[h!]
	\centering
	\includegraphics[width = 7in, height = 6in]{asia.png}
	\caption{"Simplified tectonic map of East Asia and the Western Pacific illustrating latest Cretaceous and Cenozoic faults in East Asia. 1, 2 and 3 are major thrust, strike-slip and normal fault, respectively; 4, 5 and 6 are convergent (filled triangles are for active and open triangles are for inactive boundary), transform and divergent plate boundary, respectively; 7 is land; 8 is sea, with dark grey being basin or ocean floor and light grey being continental shelf or morphological high on basin or ocean floor. BHb, Bohaiwan basin; BSb, Banda Sea basin; CKg, Central Kamchatka graben; ECSb, East China Sea basin; FMg, Fushun-Meikehou graben; Fr, Fenwei rift; HYr, Hetao-Yinchuan rift; Jb, Java basins; MGb, Mergui basin; MLb, Malay basin; OT, Okinawa Trough; Pb, Pattani basin; Sb, Sumatra basins; SCSb, South China Sea basin; SCSmb, South China Sea marginal basin; SHdsz, Sakhalin-Hokkaido dextral shear zone; SLb, Shantar-Liziansky basin; SXr, Shanxi rift; Yb, Yunqing basin; YSb, Yellow Sea basin; YYg, Yilan-Yitong graben; Zb, Zengmu basin; Zu, Zenghe uplift" \citep{Schellart2005}. The location of Figure \ref{broad} is outlined in Central Asia. }
	\label{asia}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width = 7.0in, height = 4.09in]{broad.png}
	\caption{Shaded relief map of Mongolia with fault overlays and seismic moment tensor solutions for recorded earthquakes. Important locations or faults are labeled. HTF = Hoh-Serh-Tsagaan-Salaa Fault, BF = Bolnay Fault, BGF = Bogd Fault. The study area and location of Figure \ref{intro} is outlined in black. The difference between right-lateral transpressional strike-slip in the Altai Range and left-lateral transpressional strike-slip in the Gobi-Altai is especially important. Modified after \citet{Calais2003}}
	\label{broad}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width = 7in, height = 4.2in]{intro.png}
	\caption{Landsat Imagery basemap showing important locations for this study. The large white box surrounding the Shargyn Basin is the new mapping from this study. The white area surrounding the Dariv Range indicates mapping performed by \citet{Dijkstra2006} and as a part of unpublished research by Claire Bucholz. The area surrounding the Sutai Range was mapped by \citet{Cunningham2003}. The small white boxes around the Shargyn Basin show areas that we studied in the field. The red lines are labeled cross-sections that will be discussed in the Structural Evidence section. A GPS vector near the city of Altai is shown in the northeast. Earthquake focal mechanisms in the area are also shown.}
	\label{intro}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 6in, height = 3.5in]{grain.png}
  \caption{Schematic map of the dominant structural grain in western Mongolia. The study area is boxed for reference. The shaded Junggar Block is mechanically rigid. The Junggar Block may be a trapped block of oceanic crust \citep{Carroll1990a}.  The Hangay Block consists of microcontinental fragments that accreted during the early stages of the Central Asian Orogeny. It is not shaded because it is probably not mechanically rigid.  Modified after \citet{Cunningham2005a}}
  \label{grain}
\end{figure}
\clearpage

>>>>

\begin{figure}[h!]
	\centering
	\includegraphics[width = 6in, height = 5.1in]{asia.png}
	\caption{"Simplified tectonic map of East Asia and the Western Pacific illustrating latest Cretaceous and Cenozoic faults in East Asia. 1, 2 and 3 are major thrust, strike-slip and normal fault, respectively; 4, 5 and 6 are convergent (filled triangles are for active and open triangles are for inactive boundary), transform and divergent plate boundary, respectively; 7 is land; 8 is sea, with dark grey being basin or ocean floor and light grey being continental shelf or morphological high on basin or ocean floor. BHb, Bohaiwan basin; BSb, Banda Sea basin; CKg, Central Kamchatka graben; ECSb, East China Sea basin; FMg, Fushun-Meikehou graben; Fr, Fenwei rift; HYr, Hetao-Yinchuan rift; Jb, Java basins; MGb, Mergui basin; MLb, Malay basin; OT, Okinawa Trough; Pb, Pattani basin; Sb, Sumatra basins; SCSb, South China Sea basin; SCSmb, South China Sea marginal basin; SHdsz, Sakhalin-Hokkaido dextral shear zone; SLb, Shantar-Liziansky basin; SXr, Shanxi rift; Yb, Yunqing basin; YSb, Yellow Sea basin; YYg, Yilan-Yitong graben; Zb, Zengmu basin; Zu, Zenghe uplift" \citep{Schellart2005}. The location of Figure \ref{broad} is outlined in Central Asia. }
	\label{asia}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width = 6.0in, height = 3.40in]{broad.png}
	\caption{Shaded relief map of Mongolia with fault overlays and seismic moment tensor solutions for recorded earthquakes. Important locations or faults are labeled. HTF = Hoh-Serh-Tsagaan-Salaa Fault, BF = Bolnay Fault, BGF = Bogd Fault. The study area and location of Figure \ref{intro} is outlined in black. The difference between right-lateral transpressional strike-slip in the Altai Range and left-lateral transpressional strike-slip in the Gobi-Altai is especially important. Modified after \citet{Calais2003}}
	\label{broad}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width = 6in, height = 3.6in]{intro.png}
	\caption{Landsat Imagery basemap showing important locations for this study. The large white box surrounding the Shargyn Basin is the new mapping from this study. The white area surrounding the Dariv Range indicates mapping performed by \citet{Dijkstra2006} and as a part of unpublished research by Claire Bucholz. The area surrounding the Sutai Range was mapped by \citet{Cunningham2003}. The small white boxes around the Shargyn Basin show areas that we studied in the field. The red lines are labeled cross-sections that will be discussed in the Structural Evidence section. A GPS vector near the city of Altai is shown in the northeast.}
	\label{intro}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 6in, height = 3.5in]{grain.png}
  \caption{Schematic map of the dominant structural grain in western Mongolia. The dark gray lines show the strike of the structural grain. The study area is boxed for reference. The shaded Junggar Block is mechanically rigid. The Junggar Block may be a trapped block of oceanic crust \citep{Carroll1990a}.  The Hangay Block consists of microcontinental fragments that accreted during the early stages of the Central Asian Orogeny. It is not shaded because it is probably not mechanically rigid.  Modified after \citet{Cunningham2005a}}
  \label{grain}
\end{figure}
\clearpage

### 2013-10-07 writing/jaes_article/discussion.tex
starting jaes article

	With a kinematic description of the Shargyn Basin in hand, it is interesting to ask why such structures formed in their current locations. One answer to this questions involves pre-existing weaknesses in the crust. For most of its length, the Bogd Fault closely follows the Main Mongolian Lineament. he Main Mongolian Lineament is probably a suture zone and separates a Late Proterozoic and Early Paleozoic orogeny on the north side from a Late Paleozoic orogeny on the south side. Near the stepover on the east side of the basin, the Bogd Fault bends southwards 20-30 degrees. This bend in the Bogd Fault may be due to a bend in the Main Mongolian Lineament. \citet{Windley2007} has mapped the Main Mongolian Lineament as bending southwards in this area as well. The trace of the Main Mongolian Lineament through the intersection wedge is shown in \ref{intersection_wedge_joint}. On a broader scale, the Gobi-Altai and Altai ranges both follow the approximate structural grain in Figure \ref{grain}.

>>>>

        With a kinematic description of the Shargyn Basin in hand, it is interesting to ask why such structures formed in their current locations. One answer to this questions involves pre-existing weaknesses in the crust. For most of its length, the Bogd Fault closely follows the Main Mongolian Lineament. The Main Mongolian Lineament is probably a suture zone and separates a Late Proterozoic and Early Paleozoic orogeny on the north side from a Late Paleozoic orogeny on the south side \citep{Windley2007}. Near the stepover on the east side of the basin, the Bogd Fault bends southwards 20-30 degrees. This bend in the Bogd Fault may be due to a bend in the Main Mongolian Lineament. \citet{Windley2007} has mapped the Main Mongolian Lineament as bending southwards in this area as well. The trace of the Main Mongolian Lineament through the intersection wedge is shown in \ref{intersection_wedge_joint}. On a broader scale, the Gobi-Altai and Altai ranges both follow the approximate structural grain in Figure \ref{grain}.

### 2013-10-07 writing/jaes_article/interpretation.tex
starting jaes article

\section{Structural Interpretation}
The Shargyn Basin is a combination of a conjugate strike slip fault intersection and a left-lateral compressional strike-slip stepover. The Bogd Fault to the south, the Tonhil Fault to the west, the Shargyn Fault to the north and the Khantaishir Thrusts to the east are the primary faults governing the structure of the Shargyn Basin. The Bogd Fault and the Shargyn Fault are linked in a compressional stepover by the Khantaishir Thrusts. However, some motion remains on the continuation of the Bogd Fault. The remainder of this motion is transferred into multiple thrust splays, the last of which combines with terminal thrust splays from the Tonhil Fault to form an uplifted region that I will call the intersection wedge. Similar thrust splays on the Shargyn Fault uplift the Dariv Range and link with thrust faults in the Dariv Basin and the Sutai Range. Figure \ref{schematic} shows a schematic diagram of this structure.

>>>>

\section{Interpretation}
	The Shargyn Basin is a combination of a conjugate strike slip fault intersection and a left-lateral compressional strike-slip stepover. The Bogd Fault to the south, the Tonhil Fault to the west, the Shargyn Fault to the north and the Khantaishir Thrusts to the east are the primary faults governing the structure of the Shargyn Basin. The Bogd Fault and the Shargyn Fault are linked in a compressional stepover by the Khantaishir Thrusts. However, some motion remains on the continuation of the Bogd Fault. The remainder of this motion is transferred into multiple thrust splays, the last of which combines with terminal thrust splays from the Tonhil Fault to form an uplifted region that I will call the intersection wedge. Similar thrust splays on the Shargyn Fault uplift the Dariv Range and link with thrust faults in the Dariv Basin and the Sutai Range. Figure \ref{schematic} shows a schematic diagram of this structure.

### 2013-10-07 writing/jaes_article/intro.tex
starting jaes article

\section{Motivation}
	Continental deformation can occur far from plate boundaries. The behavior of intraplate fault systems is poorly understood. Furthermore, where multiple fault systems intersect, complex kinematics can occur. Understanding how and why these kinematic patterns develop is important for understanding broad active tectonic patterns, reconstructing past tectonics, analyzing seismic hazard and identifying potential resources.

	In this paper, I examine the intersection of the Altai Range and the Gobi-Altai Range. The Altai Range and the Gobi-Altai Range are two large, actively forming mountain ranges in central Asia. The Altai Range is characterized by right-lateral transpressional slip, while the Gobi-Altai Range is characterized by left-lateral transpressional slip \citep{Cunningham2005a}\citep{Cunningham2010}. The intersection of these two fault systems provides a natural laboratory for studying strike-slip kinematics in an area with a long, varied tectonic history. Furthermore, an understanding of this critical zone will help elucidate the evolution of regional tectonic patterns.

	The 150 km wide Shargyn Basin in western Mongolia lies at the intersection of the Altai fault system and the Gobi-Altai fault system. Here, I describe the Shargyn Basin as the result of transpressional strike-slip kinematics. The kinematics consist of a compressional strike-slip stepover, a conjugate strike-slip intersection, and termination thrust splays. I also discuss the active faulting in the context of pre-existing foliation and structural weaknesses.

>>>>

\section{Introduction}
	Continental deformation can occur far from plate boundaries. The behavior of intraplate fault systems is poorly understood. Furthermore, where multiple fault systems intersect, complex kinematics can occur. Understanding how and why these kinematic patterns develop is important for understanding broad active tectonic patterns, reconstructing past tectonics, analyzing seismic hazard and identifying potential resources.

	In this paper, we examine the intersection of the Altai Range and the Gobi-Altai Range. The Altai Range and the Gobi-Altai Range are two large, actively forming mountain ranges in central Asia. The Altai Range is characterized by right-lateral transpressional slip, while the Gobi-Altai Range is characterized by left-lateral transpressional slip \citep{Cunningham2005a}\citep{Cunningham2010}. The intersection of these two fault systems provides a natural laboratory for studying strike-slip kinematics in an area with a long, varied tectonic history. Furthermore, an understanding of this critical zone will help elucidate the evolution of regional tectonic patterns.

	The 150 km wide Shargyn Basin in western Mongolia lies at the intersection of the Altai fault system and the Gobi-Altai fault system. Here, we describe the Shargyn Basin as the result of transpressional strike-slip kinematics. The kinematics consist of a compressional strike-slip stepover, a conjugate strike-slip intersection, and termination thrust splays. We also discuss the active faulting in the context of pre-existing foliation and structural weaknesses.

### 2013-10-07 writing/jaes_article/main.tex
starting jaes article

\documentclass[12pt, doublepage, vi]{mitthesis}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[margin=0.75in]{geometry}
\usepackage{setspace}
\renewcommand\thechapter{}
\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\begin{document}
\title{Active deformation of the Shargyn Basin, a transpressional strike-slip intersection in western Mongolia.}
\author{Thomas Ben Thompson}
\department{Department of Earth, Atmospheric and Planetary Science}
\degree{Bachelor of Science in Earth, Atmospheric and Planetary Sciences}
\degreemonth{June}
\degreeyear{2013}
\copyrightnotice{Thomas Ben Thompson}
\thesisdate{May 10, 2013}
\supervisor{Oliver Jagoutz}{Assistant Professor}
\chairman{Richard P. Binzel}{Chair, Committee on Undergraduate Program}
\maketitle
\include{abstract}

\section*{Acknowledgments}
Primarily, I thank Claire Bucholz (EAPS PhD candidate) for wandering the Mongolian steppes and mountains and teaching me endlessly about geology and EAPS Professor Oliver Jagoutz for supervising and helping me through the whole thesis process. I thank the UROP office and the EAPS department for supporting my field work in Mongolia last summer. I also thank Yeson Erdene and Agi.

\tableofcontents
\listoffigures
\clearpage
\include{intro}
\include{background}
\include{structure}
\include{discussion}
\include{conclusion}
\appendix
\include{xsecappendix}
\bibliographystyle{plainnat}
\bibliography{/home/tbent/projects/library.bib}

>>>>

\documentclass[12pt]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[margin=1.0in]{geometry}
\usepackage{setspace}
\usepackage{caption}
\doublespacing
\AtBeginCaption{\doublespacing}
\begin{document}
\title{Active deformation of the Shargyn Basin, a transpressional strike-slip intersection in western Mongolia.}
\author{%
    Thomas Ben Thompson (Corresponding Author)\\
    Department of Earth, Atmospheric and Planetary Sciences at MIT\\
    \texttt{tthompson@fas.harvard.edu}\vspace{40pt} \\
    Oliver Jagoutz \\
    Department of Earth, Atmospheric and Planetary Sciences at MIT \\
    \texttt{jagoutz@mit.edu} \vspace{40pt} \\
    Claire Bucholz \\ 
    Department of Earth, Atmospheric and Planetary Sciences at MIT \\
    \texttt{cbucholz@mit.edu} \\
    }
\maketitle

\include{abstract}

\tableofcontents
\listoffigures
\clearpage
\include{intro}
\include{background}
\include{structure}
\include{discussion}
\include{conclusion}
\appendix
\include{xsecappendix}
\section*{Acknowledgments}
Many thanks to Yeson Erdene, a student at MUST, and Agi, our friend and driver. 
\bibliographystyle{plainnat}
\bibliography{/home/tbent/projects/library.bib}

### 2013-10-07 writing/jaes_article/structure.tex
starting jaes article

\begin{figure}[h!]
  \centering
  \includegraphics[width = 7in, height = 5.0in]{fault_map.png}
  \caption{A map of the Shargyn Basin showing the studied faults and important locations. Slip is indicated by thrust teeth or lateral slip arrows.}
  \label{faultmap}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 7in, height = 6.83in]{haliun_joint.png}
  \caption{A cross-section through the Haliun Thrust and Butara Thrust paired with a Landsat image. Important locations and lithology are noted on the satellite image.}
  \label{haliun_joint}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 6in, height = 7.68in]{intersection_wedge_joint.png}
  \caption{Landsat imagery showing the intersection wedge area at the southwestern corner of the Shargyn Basin. Mapped active faults are shown by solid red lines. Slip sense is shown with thrust teeth or lateral slip arrows. The Main Mongolian Lineament is marked by the dark black line -- dashed red and black where it overlaps with a fault. Note the two conjugate strike-slip faults, the stacked thrusts at the basin margin and the two small transtensional basins located at the eastern and northern corners of the wedge. Cross sections C-C' and D-D' through the transtensional basin and the intersection wedge are shown. Cross-sections X2-X2' and X3-X3' are shown in Appendix A.}
  \label{intersection_wedge_joint}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 7in, height = 7.5in]{lil_dariv_joint.png}
  \caption{A cross-section through the Little Dariv Mountain area paired with a Landsat image of the surrounding area. Important locations and lithology are noted on the satellite image.}
  \label{lil_dariv_joint}
\end{figure}
\clearpage
The western end of the Shargyn Fault, nicknamed Little Dariv Mountain, exhibits thrusts in a small positive flower structure, seen in cross-section E-E' in Figure \ref{lil_dariv_joint}. The positive flower structure has been identified by previous researchers \citep{Howard2006}. Their interpretation is similar to the one discussed here. However, there are differences in the number and location of thrusts. To the north of the Shargyn Basin is the Dariv Basin, a much smaller, higher elevation basin. Little Dariv Mountain is located on the boundary of these two basins. The majority of the mountain is composed of greenschist-facies sedimentary and volcanic rocks. On the northern side of the range, there is a 100 meter thick band of folded carbonates and marls. Separating the range is a thrust fault. The fault follows a valley that is clearly visible on satellite imagery. To the south of the fault is a steep 200 meter topographic rise, indicating that the fault dips southwards. No other faults were identifiable in the core of Little Dariv Mountain.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 7in, height = 6.85in]{neshargyn_joint.png}
  \caption{A cross-section through the Shargyn Fault in the northeast corner of the Shargyn Basin paired with a Landsat image of the surrounding area. Important locations and lithology are noted on the satellite image.}
  \label{neshargyn_joint}
\end{figure}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width = 6in, height = 4.2in]{fault_map.png}
  \caption{A map of the Shargyn Basin showing the studied faults and important locations. Slip is indicated by thrust teeth or lateral slip arrows.}
  \label{faultmap}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 6in, height = 5.83in]{haliun_joint.png}
  \caption{A cross-section through the Haliun Thrust and Butara Thrust paired with a Landsat image. Important locations and lithology are noted on the satellite image.}
  \label{haliun_joint}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width = 5in, height = 6.68in]{intersection_wedge_joint.png}
  \caption{Landsat imagery showing the intersection wedge area at the southwestern corner of the Shargyn Basin. Mapped active faults are shown by solid red lines. Slip sense is shown with thrust teeth or lateral slip arrows. The Main Mongolian Lineament is marked by the dark black line -- dashed red and black where it overlaps with a fault. Note the two conjugate strike-slip faults, the stacked thrusts at the basin margin and the two small transtensional basins located at the eastern and northern corners of the wedge. Cross sections C-C' and D-D' through the transtensional basin and the intersection wedge are shown. Cross-sections X2-X2' and X3-X3' are shown in Appendix A.}
  \label{intersection_wedge_joint}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 6in, height = 6.6in]{lil_dariv_joint.png}
  \caption{A cross-section through the Little Dariv Mountain area paired with a Landsat image of the surrounding area. Important locations and lithology are noted on the satellite image.}
  \label{lil_dariv_joint}
\end{figure}
\clearpage
The western end of the Shargyn Fault, nicknamed Little Dariv Mountain, exhibits thrusts in a small positive flower structure, seen in cross-section E-E' in Figure \ref{lil_dariv_joint}. The positive flower structure has been identified by previous researchers \citep{Howard2006}. Their interpretation is similar to the one discussed here. However, there are differences in the number and location of thrusts. To the north of the Shargyn Basin is the Dariv Basin, a much smaller, higher elevation basin. Little Dariv Mountain is located on the boundary of these two basins. The majority of the mountain is composed of greenschist-facies sedimentary and volcanic rocks. On the northern side of the range, there is a 100 meter thick band of folded carbonates and marls. Separating the range is a thrust fault. The fault follows a valley that is clearly visible on satellite imagery. To the south of the fault is a steep 200 meter topographic rise, indicating that the fault dips southwards. No other faults were identifiable in the core of Little Dariv Mountain.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 6in, height = 5.85in]{neshargyn_joint.png}
  \caption{A cross-section through the Shargyn Fault in the northeast corner of the Shargyn Basin paired with a Landsat image of the surrounding area. Important locations and lithology are noted on the satellite image.}
  \label{neshargyn_joint}
\end{figure}
